\documentclass[ebook,11pt,oneside,openany]{memoir}
\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}
\usepackage{savetrees}
\usepackage{verbatim}
\linespread{1.6}
\setlength{\footskip}{20pt}

\newcommand{\thought}[1]{\textit{#1}}

\newcommand{\scenechange}{
  \par
  \vspace{\baselineskip}
  \par
\noindent}

\newcommand{\majorchange}{
  \par
  \vspace{\baselineskip}
  \hfill
  \textasteriskcentered
  \hfill
  \vspace{\baselineskip}
\noindent}

\title{Runner-RL: A short story}
\author{Brett Witty}

\begin{document}

\maketitle

You scurry down the street and cross over the old abandoned train lines. Your AI assistant cheerfully buzzes in your ear: ``Location data not available. Would you like directions to a nearby coffee place?'' You turn it off, hunch your shoulders against the rain and push on.

\scenechange

Ten minutes later, you're standing underneath a broken ArcoPharm sign. You check your tablet. This must be the place. A homeless man coughs in your direction.

``Optimize your algos for cash?''

You wave him away.

He struggles to get to his feet, mostly because one is missing. But you guess diabetes, not the war. ``Come on, man! I know things. Python, Go... um... C? Ruby?!''

He's bringing too much attention. You fish about in your jacket pocket for a bunch of cryptocoins you printed up this afternoon, and throw them in his direction. While he scrabbles for them, you duck into a promising-looking alleyway.

``Thanks, man! Thank y--'' He looks at the coins. ``Bitcoins?! What's the hell man? What am I supposed to do with these?''

The homeless guy recedes into the background as you dive deeper into the darkness. Up ahead, you think you spy your contact.

In the basketball court behind a block of tenements sits an abandoned GRID utility block. Perched on top is a man, cabled into the GRID, eyes covered with a VR headset. He swipes quickly at the air and does not seem to react to your presence. His dreadlocks bounce with every movement.

You quietly extend your baton and tap on the utility housing, hoping to alert him. He does not seem to notice you.

You clear your throat. ``StackPop? I saw your post.''

Still seemingly blind with his headset he says, ``Man, I seen you. I seen you since 41st street. I seen you kicking yo way through the Sprawl. I seen you with that bum. I seen you before you even thought about being seen. Eyes in the skies, man...''

You shift uneasily and spot a drone hovering far above. You wonder if you can only see it now because he lit it up.

``But,'' he says, looking at you with blank VR eyes. ``You ain't no SecCorp. You ain't no GRID sucka.'' StackPop leaps down from the utility block and taps his headset, turning it into a clear visor. He whips a phosporescent blue light in your eyes. You grimace but don't flinch away.

``And you ain't no goddamn Mask or augment, thank Bezos. Whatchu want?''

``Exit nodes. Sumitomo subsidiary called CloudHutch. Based out of Cali Republic.''

StackPop looks you up and down. ``You want zaibatsu intel? \textit{Sumitomo intel}? Oh damn, you better be fronting.''

``Real deal. I need at least two exit nodes. Non-GRID. No Collective, Sealand or Soviet links. Active immediately. ZKP blockchain contract and active proof you scrubbed your machines of the details.''

StackPop flips his visor at you. ``Daaaamn.'' He composes himself. ``Gonna cost you.''

You put your baton away and pull out a card. You tap it to the subdermal cryptolock in your forearm. ``Keys to a stash of GRID repos. Core IP. White papers on new protocols. Some old projects from before the merger. 5 years of dev, 10 Terabytes of source.''

``I don't know who you are, man...'' he says, arms wide. ``But you got yourself a deal!''


\end{document}
